5. Blas, J., Abaurrea, T., D'Amico, M., Barcellona, F., Revilla, E., Roman, J. \&  Carrete, M. (2016) Management-related traffic as a stressor eliciting parental care in a roadside-nesting bird: the european bee-eater \textit{Merops apiaster}. \textit{Plos One},  \textbf{11}, e0164371.

10. Young, R.C., Barger, C.P., Dorresteijn, I., Haussmann, M.F. \&  Kitaysky, A.S. (2016) Telomere length and environmental conditions predict stress levels but not parental investment in a long-lived seabird. \textit{Marine Ecology Progress Series},  \textbf{556}, 251-259.

11. Barger, C.P., Young, R.C., Will, A., Ito, M. \&  Kitaysky, A.S. (2016) Resource partitioning between sympatric seabird species increases during chick-rearing. \textit{Ecosphere},  \textbf{7}, e01447.

19. Auer, S.A., Islam, K., Wagner, J.R., Summerville, K.S. \&  Barnes, K.W. (2016) The diet of cerulean warbler (\textit{Setophaga cerulea}) nestlings and adult nest provisioning behaviors in southern indiana. \textit{Wilson Journal Of Ornithology},  \textbf{128}, 573-583.

22. Amininasab, S.M., Kingma, S.A., Birker, M., Hildenbrandt, H. \&  Komdeur, J. (2016) The effect of ambient temperature, habitat quality and individual age on incubation behaviour and incubation feeding in a socially monogamous songbird. \textit{Behavioral Ecology And Sociobiology},  \textbf{70}, 1591-1600.

24. Koenig, W.D. \&  Walters, E.L. (2016) Provisioning patterns in the cooperatively breeding acorn woodpecker: does feeding behaviour serve as a signal? \textit{Animal Behaviour},  \textbf{119}, 125-134.

27. Cantarero, A., Lopez-Arrabe, J., Plaza, M., Saavedra-Garces, I. \&  Moreno, J. (2016) Males feed their mates more and take more risks for nestlings with larger female-built nests: an experimental study in the nuthatch \textit{Sitta europaea}. \textit{Behavioral Ecology And Sociobiology},  \textbf{70}, 1141-1150.

28. Schroeder, J., Hsu, Y.H., Winney, I., Simons, M., Nakagawa, S. \&  Burke, T. (2016) Predictably philandering females prompt poor paternal provisioning. \textit{American Naturalist},  \textbf{188}, 219-230.

29. Tanaka, K.D., Morimoto, G. \&  Ueda, K. (2016) Equivocal responses of feeding parents to experimental brood sizes in a hawk-cuckoo host: brood size as a reference for parental provisioning decisions? \textit{Ethology},  \textbf{122}, 640-648.

33. Ren, Q.M., Luo, S., Du, X.J., Chen, G.L., Song, S. \&  Du, B. (2016) Helper effects in the azure-winged magpie cyanopica cyana in relation to highly-clumped nesting pattern and high frequency of conspecific nest-raiding. \textit{Journal Of Avian Biology},  \textbf{47}, 449-456.

35. Scioscia, G., Rey, A.R. \&  Schiavini, A. (2016) Breeding biology of magellanic penguins (\textit{Spheniscus magellanicus}) at the beagle channel: interannual variation and its relationship with foraging behaviour. \textit{Journal Of Ornithology},  \textbf{157}, 773-785.

37. Romano, A., Bazzi, G., Caprioli, M., Corti, M., Costanzo, A., Rubolini, D. \&  Saino, N. (2016) Nestling sex and plumage color predict food allocation by barn swallow parents. \textit{Behavioral Ecology},  \textbf{27}, 1198-1205.

38. Liebl, A.L., Browning, L.E. \&  Russell, A.F. (2016) Manipulating carer number versus brood size: complementary but not equivalent ways of quantifying carer effects on offspring. \textit{Behavioral Ecology},  \textbf{27}, 1247-1254.

40. Endo, S. \&  Ueda, K. (2016) Factors affecting female incubation behavior in the bullheaded shrike. \textit{Ornithological Science},  \textbf{15}, 151-161.

42. Dzielski, S.A., Van Doren, B.M., Hruska, J.P. \&  Hite, J.M. (2016) Reproductive biology of the Sapayoa (\textit{Sapayoa aenigma}), the "old world suboscine" of the new world. \textit{Auk},  \textbf{133}, 347-363.

43. Carla, M.R. \&  Fontana, C.S. (2016) Breeding biology of the tropeiro seedeater (\textit{Sporophila beltoni}). \textit{Auk},  \textbf{133}, 484-496.

54. Yasukawa, K., Berrios, H.K. \&  Johannes, A.W. (2016) A test of the nestling discrimination hypothesis for parasitism of red-winged blackbirds (\textit{Agelaius phoeniceus}) by brown-headed cowbirds (molothrus ater). \textit{Wilson Journal Of Ornithology},  \textbf{128}, 437-441.

55. Hanson, M.R. \&  Baldwin, J.D. (2016) Provisioning rates suggest food limitation for breeding bald eagles in their southernmost range. \textit{Southeastern Naturalist},  \textbf{15}, 365-381.

67. Lucass, C., Eens, M. \&  Muller, W. (2016) When ambient noise impairs parent-offspring communication. \textit{Environmental Pollution},  \textbf{212}, 592-597.

69. Lucass, C., Iserbyt, A., Eens, M. \&  Muller, W. (2016) Structural (uv) and carotenoid-based plumage coloration signals for parental investment? \textit{Ecology And Evolution},  \textbf{6}, 3269-3279.

70. Liebl, A.L., Nomano, F.Y., Browning, L.E. \&  Russell, A.F. (2016) Experimental evidence for fully additive care among male carers in the cooperatively breeding chestnut-crowned babbler. \textit{Animal Behaviour},  \textbf{115}, 47-53.

73. Cornell, A. \&  Williams, T.D. (2016) Individual quality and double-brooding in a highly synchronous songbird population. \textit{Auk},  \textbf{133}, 251-260.

75. Potticary, A.L., Dowling, J.L., Barron, D.G., Baldassarre, D.T. \&  Webster, M.S. (2016) Subtle benefits of cooperation to breeding males of the red-backed fairywren. \textit{Auk},  \textbf{133}, 286-297.

76. Burtka, J.L., Lovern, M.B. \&  Grindstaff, J.L. (2016) Baseline hormone levels are linked to reproductive success but not parental care behaviors. \textit{General And Comparative Endocrinology},  \textbf{229}, 92-99.

85. Pretelli, M.G., Isacch, J.P. \&  Cardoni, D.A. (2016) Variation in parental care in the spectacled tyrant \textit{Hymenops perspicillatus} is associated with increased nest predation in grassland fragments. \textit{Journal Of Ornithology},  \textbf{157}, 451-460.

86. Morrison, K.W., Morrison, N.C., Buchheit, R.M., Dunn, R., Battley, P.F. \&  Thompson, D.R. (2016) The canalized parental roles of a Eudyptes penguin constrain provisioning and growth of chicks during nutritional stress. \textit{Behavioral Ecology And Sociobiology},  \textbf{70}, 467-479.

87. Moks, K., Tilgar, V., Thomson, R.L., Calhim, S., Jarvisto, P.E., Schuett, W., Velmala, W. \&  Laaksonen, T. (2016) Predator encounters have spatially extensive impacts on parental behaviour in a breeding bird community. \textit{Proceedings Of The Royal Society B-biological Sciences},  \textbf{283}, 20160020.

92. Ostreiher, R. \&  Heifetz, A. (2016) The blessing of having younger nestmates: the case of the arabian babbler. \textit{Behavioral Ecology},  \textbf{27}, 393-400.

94. Bebbington, K. \&  Hatchwell, B.J. (2016) Coordinated parental provisioning is related to feeding rate and reproductive success in a songbird. \textit{Behavioral Ecology},  \textbf{27}, 652-659.

96. Heist, C.A. \&  Ritchison, G. (2016) Effects of variation in nestling hunger levels and begging on the provisioning behavior of male and female eastern phoebes (\textit{Sayornis phoebe}). \textit{Wilson Journal Of Ornithology},  \textbf{128}, 132-143.

97. Botero-Delgadillo, E. \&  Vasquez, R.A. (2016) Nest architecture, clutch size, nestling growth patterns and nestling attendance of the fire-eyed diucon (\textit{Xolmis pyrope}) in north-central chile. \textit{Wilson Journal Of Ornithology},  \textbf{128}, 184-190.

100. Michalczuk, J. \&  Michalczuk, M. (2016) Differences in reproductive investment between male and female syrian woodpeckers \textit{Dendrocopos syriacus} (hemprich and ehrenberg, 1833) in a newly-colonised area. \textit{Acta Zoologica Bulgarica},  \textbf{68}, 77-84.

101. Fronstin, R.B., Christians, J.K. \&  Williams, T.D. (2016) Experimental reduction of haematocrit affects reproductive performance in european starlings. \textit{Functional Ecology},  \textbf{30}, 398-409.

102. Sanchez-Martinez, M.A. \&  Londono, G.A. (2016) Nesting behavior of male and female undulated antshrikes (\textit{Frederickena unduliger}). \textit{Journal Of Field Ornithology},  \textbf{87}, 21-28.

105. Mainwaring, M.C. \&  Hartley, I.R. (2016) Experimentally reduced nest-building costs result in higher provisioning rates but not increased offspring fitness in blue tits. \textit{Avian Biology Research},  \textbf{9}, 52-57.

114. Lucass, C., Korsten, P., Eens, M. \&  Muller, W. (2016) Within-family parent-offspring co-adaptation in a wild bird: on static traits, behavioural reaction norms, and sex differences. \textit{Functional Ecology},  \textbf{30}, 274-282.

120. Robertson, G.S., Bolton, M. \&  Monaghan, P. (2016) Influence of diet and foraging strategy on reproductive success in two morphologically similar sympatric seabirds. \textit{Bird Study},  \textbf{63}, 319-329.

124. Chutter, C.M., Redmond, L.J., Cooper, N.W., Dolan, A.C., Duffield, D. \&  Murphy, M.T. (2016) Paternal behaviour in a socially monogamous but sexually promiscuous Passerine bird. \textit{Behaviour},  \textbf{153}, 443-466.

126. Bueno-Enciso, J., Ferrer, E.S., Barrientos, R., Serrano-Davies, E. \&  Sanz, J.J. (2016) Habitat fragmentation influences nestling growth in mediterranean blue and great tits. \textit{Acta Oecologica-international Journal Of Ecology},  \textbf{70}, 129-137.

131. Kadin, M., Olsson, O., Hentati-Sundberg, J., Ehrning, E.W. \&  Blenckner, T. (2016) Common guillemot \textit{Uria aalge} parents adjust provisioning rates to compensate for low food quality. \textit{Ibis},  \textbf{158}, 167-178.

136. McDonald, P.G., Rollins, L.A. \&  Godfrey, S. (2016) The relative importance of spatial proximity, kin selection and potential 'greenbeard' signals on provisioning behaviour among helpers in a cooperative bird. \textit{Behavioral Ecology And Sociobiology},  \textbf{70}, 133-143.

137. Dakin, R., Lendvai, A.Z., Ouyang, J.Q., Moore, I.T. \&  Bonier, F. (2016) Plumage colour is associated with partner parental care in mutually ornamented tree swallows. \textit{Animal Behaviour},  \textbf{111}, 111-118.

139. Exposito-Granados, M., Parejo, D. \&  Aviles, J.M. (2016) Sex-specific parental care in response to predation risk in the european roller, \textit{Coracias garrulus}. \textit{Ethology},  \textbf{122}, 72-79.

148. Du, B., Guan, M.M., Ren, Q.M. \&  Chen, G.L. (2015) Cuckolded male ground tits increase parental care for the brood. \textit{Animal Behaviour},  \textbf{110}, 61-67.

150. Wetzel, D.P., Hatch, M.I. \&  Westneat, D.F. (2015) Genetic sources of individual variation in parental care behavior. \textit{Behavioral Ecology And Sociobiology},  \textbf{69}, 1933-1943.

151. Cram, D.L., Blount, J.D. \&  Young, A.J. (2015) The oxidative costs of reproduction are group-size dependent in a wild cooperative breeder. \textit{Proceedings Of The Royal Society B-biological Sciences},  \textbf{282}, 20152031.

153. Lendvai, A.Z., Akcay, C., Ouyang, J.Q., Dakin, R., Domalik, A.D., St John, P.S., Stanback, M., Moore, I.T. \&  Bonier, F. (2015) Analysis of the optimal duration of behavioral observations based on an automated continuous monitoring system in tree swallows (\textit{Tachycineta bicolor}): is one hour good enough? \textit{Plos One},  \textbf{10}, e0141194.

160. Leonard, M.L., Horn, A.G., Oswald, K.N. \&  McIntyre, E. (2015) Effect of ambient noise on parent-offspring interactions in tree swallows. \textit{Animal Behaviour},  \textbf{109}, 1-7.

163. Ouyang, J.Q., Lendvai, A.Z., Dakin, R., Domalik, A.D., Fasanello, V.J., Vassallo, B.G., Haussmann, M.F., Moore, I.T. \&  Bonier, F. (2015) Weathering the storm: parental effort and experimental manipulation of stress hormones predict brood survival. \textit{Bmc Evolutionary Biology},  \textbf{15}, 219.

164. Dunn, J.C., Hamer, K.C. \&  Benton, T.G. (2015) Anthropogenically-mediated density dependence in a declining farmland bird. \textit{Plos One},  \textbf{10}, e0139492.

166. Laubach, Z.M., Perng, W., Lombardo, M., Murdock, C. \&  Foufopoulos, J. (2015) Determinants of parental care in mountain white-crowned sparrows (\textit{Zonotrichia leucophrys} oriantha). \textit{Auk},  \textbf{132}, 893-902.

172. Wiebe, K.L. \&  Slagsvold, T. (2015) Foraging trade-offs between prey size, delivery rate and prey type: how does niche breadth and early learning of the foraging niche affect food delivery? \textit{Ethology},  \textbf{121}, 1010-1017.

174. Llambias, P.E., Carro, M.E. \&  Fernandez, G.J. (2015) Latitudinal differences in life-history traits and parental care in northern and southern temperate zone house wrens. \textit{Journal Of Ornithology},  \textbf{156}, 933-942.

178. Rouaiguia, M., Lahlah, N., Bensaci, E. \&  Houhamdi, M. (2015) Feeding behaviour and the role of insects in the diet of northern house-martin (\textit{Delichon urbica} meridionalis) nestlings in northeastern algeria. \textit{African Entomology},  \textbf{23}, 329-341.

181. Chiarani, E. \&  Fontana, C.S. (2015) Breeding biology of the lesser grass-finch (\textit{Emberizoides ypiranganus}) in southern brazilian upland grasslands. \textit{Wilson Journal Of Ornithology},  \textbf{127}, 441-456.

184. Fowler, M.A. \&  Williams, T.D. (2015) Individual variation in parental workload and breeding productivity in female european starlings: is the effort worth it? \textit{Ecology And Evolution},  \textbf{5}, 3585-3599.

190. Yoon, J., Ha, H.S., Jung, J.S. \&  Park, S.R. (2015) Post-mating sexual behaviors of oriental storks (\textit{Ciconia boyciana}) in captivity. \textit{Zoological Science},  \textbf{32}, 331-335.

191. Riehl, C. \&  Strong, M.J. (2015) Social living without kin discrimination: experimental evidence from a communally breeding bird. \textit{Behavioral Ecology And Sociobiology},  \textbf{69}, 1293-1299.

194. Adams, M.J., Robinson, M.R., Mannarelli, M.E. \&  Hatchwell, B.J. (2015) Social genetic and social environment effects on parental and helper care in a cooperatively breeding bird. \textit{Proceedings Of The Royal Society B-biological Sciences},  \textbf{282}, 20150689.

195. Robertson, G.S., Bolton, M. \&  Monaghan, P. (2015) Parental resource allocation among offspring varies with increasing brood age in black-legged kittiwakes \textit{Rissa tridactyla}. \textit{Bird Study},  \textbf{62}, 303-314.

196. Whytock, R.C., Davis, D., Whytock, R.T., Burgess, M.D., Minderman, J. \&  Mallord, J.W. (2015) Wood warbler \textit{Phylloscopus sibilatrix} nest provisioning rates are correlated with seasonal caterpillar availability in british oak quercus woodlands. \textit{Bird Study},  \textbf{62}, 339-347.

200. Nomano, F.Y., Browning, L.E., Savage, J.L., Rollins, L.A., Griffith, S.C. \&  Russell, A.F. (2015) Unrelated helpers neither signal contributions nor suffer retribution in chestnut-crowed babblers. \textit{Behavioral Ecology},  \textbf{26}, 986-995.

201. Grunst, A.S. \&  Grunst, M.L. (2015) Context-dependent relationships between multiple sexual pigments and paternal effort. \textit{Behavioral Ecology},  \textbf{26}, 1170-1179.

213. Rishworth, G.M. \&  Pistorius, P.A. (2015) Protection and provisioning: the role of parental behaviour in terms of chick growth and survival in a pelagic seabird. \textit{Marine Ecology Progress Series},  \textbf{530}, 153-162.

215. Auclair, M.M.M., Ono, K.A. \&  Perlut, N.G. (2015) Brood provisioning and nest survival of \textit{Ardea herodias} (great blue heron) in maine. \textit{Northeastern Naturalist},  \textbf{22}, 307-317.

223. Welch, B.C. \&  Boal, C.W. (2015) Prey use and provisioning rates of urban-nesting mississippi kites in west texas. \textit{Journal Of Raptor Research},  \textbf{49}, 141-151.

224. Bowers, E.K., Bowden, R.M., Sakaluk, S.K. \&  Thompson, C.F. (2015) Immune activation generates corticosterone-mediated terminal reproductive investment in a wild bird. \textit{American Naturalist},  \textbf{185}, 769-783.

227. Bolopo, D., Canestrari, D., Roldan, M., Baglione, V. \&  Soler, M. (2015) High begging intensity of great spotted cuckoo nestlings favours larger-size crow nest mates. \textit{Behavioral Ecology And Sociobiology},  \textbf{69}, 873-882.

233. Wegmann, M., Voegeli, B. \&  Richner, H. (2015) Oxidative status and reproductive effort of great tits in a handicapping experiment. \textit{Behavioral Ecology},  \textbf{26}, 747-754.

245. Du, B., Liu, C.J. \&  Bao, S.J. (2015) Begging form and growth pattern of nestlings correlate with parental food-allocation patterns in the horned lark (\textit{Eremophila alpestris}). \textit{Canadian Journal Of Zoology},  \textbf{93}, 273-279.

246. Diniz, P., Ramos, D.M. \&  Macedo, R.H. (2015) Attractive males are less than adequate dads in a multimodal signalling Passerine. \textit{Animal Behaviour},  \textbf{102}, 109-117.

253. Wegmann, M., Voegeli, B. \&  Richner, H. (2015) Physiological responses to increased brood size and ectoparasite infestation: adult great tits favour self-maintenance. \textit{Physiology & Behavior},  \textbf{141}, 127-134.

254. Montoya, B. \&  Torres, R. (2015) Male skin color signals direct and indirect benefits in a species with biparental care. \textit{Behavioral Ecology},  \textbf{26}, 425-434.

262. Mullers, R.H.E. \&  Amar, A. (2015) Parental nesting behavior, chick growth and breeding success of shoebills (\textit{Balaeniceps rex}) in the bangweulu wetlands, zambia. \textit{Waterbirds},  \textbf{38}, 1-9.

274. Bodrati, A., Cockle, K.L., Di Sallo, F.G., Ferreyra, C., Salvador, S.A. \&  Lammertink, M. (2015) Nesting and social roosting of the ochre-collared piculet (\textit{Picumnus temminckii}) and white-barred piculet (Picumnus cirratus), and implications for the evolution of woodpecker (picidae) breeding biology. \textit{Ornitologia Neotropical},  \textbf{26}, 223-244.

278. Jimeno, B. \&  Gil, D. (2015) Parent-absent calls are related to nestling reaction time and parental food allocation in the spotless starling. \textit{Behaviour},  \textbf{152}, 1413-1431.

279. Goyert, H.F. (2015) Foraging specificity and prey utilization: evaluating social and memory-based strategies in seabirds. \textit{Behaviour},  \textbf{152}, 861-895.

281. Oberg, M., Arlt, D., Part, T., Laugen, A.T., Eggers, S. \&  Low, M. (2015) Rainfall during parental care reduces reproductive and survival components of fitness in a Passerine bird. \textit{Ecology And Evolution},  \textbf{5}, 345-356.

282. Grunst, A.S., Grunst, M.L. \&  Rotenberry, J.T. (2015) Sexual pigmentation and parental risk-taking in yellow warblers \textit{Setophaga petechia}. \textit{Journal Of Avian Biology},  \textbf{46}, 9-17.

283. Schneider, N.A. \&  Griesser, M. (2015) Within-season increase in parental investment in a long-lived bird species: investment shifts to maximize successful reproduction? \textit{Journal Of Evolutionary Biology},  \textbf{28}, 231-240.

288. Garcia-Navas, V., Valera, F. \&  Griggio, M. (2015) Nest decorations: an 'extended' female badge of status? \textit{Animal Behaviour},  \textbf{99}, 95-107.

